---
title: "Exploring mtcars dataset"
author: "ArunPrasanna"
date: "7/10/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## mtcars dataset

``mtcars`` is a standard dataset, that contains information on various parameters related to car performance and engine capacity

```{r mtcars, echo=TRUE}
library(datasets)
head(mtcars)
```

## Shiny App to explore mtcars

- An app is created to see factors affecting mileage
- The factors considered here are
  - horse power
  - weight
  - displacement
  - No. of Cylinders

- Next we shall look into ``ui.R`` and ``server.R`` to create shinyApp

## ui.R

```{r, echo = TRUE, eval=FALSE}
library(shiny)
library(ggplot2)
shinyUI(fluidPage(
  titlePanel("Explore mtcars dataset"),
  sidebarLayout(
    sidebarPanel(
      selectInput("inputDF","Enter Y to plot vs mpg",choices = c('wt','disp','hp'))
    ),
    mainPanel(plotOutput("plot1")
              )
  )
))
```

## server.R

```{r, echo=TRUE, eval=FALSE}
shinyServer(function(input, output) {
  
  output$plot1 <- renderPlot({
    ggplot(data=mtcars, aes_string(x='mpg', y=input$inputDF, col='factor(cyl)')) +
      geom_point() + 
      geom_smooth(method="lm")
  })
})
```

App can be accessed in [Click on link !]

https://arunprasanna83.shinyapps.io/DemoApp/

It takes few seconds for plot to appear !

## Summary

- App can be viewed in https://arunprasanna83.shinyapps.io/DemoApp/
- Plot shows how the variables affect mpg with no. of cylinders in consideration
- As the weight of the car decreases, mileage increases with increase in number of cylinder
- Displacement decreases with mileage, except when 6 cylinders are used
- Horse power also show similar relation to mileage with displacement. 

